---
title: "R Notebook"
output: html_notebook
---


```{r, message=FALSE, warning=FALSE}
library(mdsr)
library(stringr)
library(ggrepel)
library(boot)
```

```{r}
j = mean(X_LeagueofLegends$gamelength)
paste("The average length of these games (in minutes) was: ", j, collapse = "")
```
#Baron only spawns starting at 20 mins in. After death it after 7 minutes

```{r}
#make a scatterplot of the game durations

g_gameLengths <- ggplot(data = X_LeagueofLegends, aes(x = X_LeagueofLegends$gamelength) ) + geom_histogram(binwidth = 1.5)
g_gameLengths

```

#First we must calculate the win ratio of each team
```{r}
#Step 1: Calculate/Tally each teams # of wins OR win ratio
teamsGamesPlayed <- X_LeagueofLegends %>%
  select(blueTeamTag, bResult, rResult, redTeamTag)
  
  View(teamsGamesPlayed)
```

```{r}
#Isolate the unique names of the blue teams
blueTeamsNames <- teamsGamesPlayed %>%
  #df <- unique(teamsGamesPlayed$blueTeamTag)
  group_by(blueTeamTag) %>%
  summarise()
View(blueTeamsNames)
```

```{r}
#Isolate the unique names of the red teams
redTeamsNames <- teamsGamesPlayed %>%
  #df <- unique(teamsGamesPlayed$blueTeamTag)
  group_by(redTeamTag) %>%
  summarise()
View(redTeamsNames)
#add some NAs for the next chunk:
redTeamsNames <- rbind( redTeamsNames, data.frame("redTeamTag"=NA))
redTeamsNames <- rbind( redTeamsNames, data.frame("redTeamTag"=NA))
```

```{r}
#combine the two columns into one list of names
teamNames <- data.frame(teamTags = coalesce(blueTeamsNames$blueTeamTag, redTeamsNames$redTeamTag))
View(teamNames)
```

```{r}
#count of the amount of wins per team on BLUE SIDE
blueTeamWins <- teamsGamesPlayed %>%
  filter(bResult == 1) %>%
  group_by(blueTeamTag) %>%
  summarise(WinsPerTeam = sum(bResult))
  View(blueTeamWins)
```

```{r}
#count of the amount of wins per team on RED SIDE
redTeamWins <- teamsGamesPlayed %>%
  filter(rResult == 1) %>%
  group_by(redTeamTag) %>%
  summarise(WinsPerTeam = sum(rResult))
  View(redTeamWins)
```


```{r}
#count of the amount of losses per team on BLUE SIDE
blueTeamLosses <- teamsGamesPlayed %>%
  filter(bResult == 0) %>%
  group_by(blueTeamTag) %>%
  summarise(LossesPerTeam = n())
  View(blueTeamLosses)
```

```{r}
#count of the amount of losses per team on RED SIDE
redTeamLosses <- teamsGamesPlayed %>%
  filter(rResult == 0) %>%
  group_by(redTeamTag) %>%
  summarise(LossesPerTeam = n())
  View(redTeamLosses)
```


```{r}
teamWins <- blueTeamWins %>%
#<- data.frame(teamTags = teamNames$teamTags, wins = "", losses = "", winLossRatio = "") %>%
  left_join(redTeamWins, by = c("blueTeamTag" = "redTeamTag")) 
View(teamWins)

```

```{r}
teamLosses <- blueTeamLosses %>%
#<- data.frame(teamTags = teamNames$teamTags, wins = "", losses = "", winLossRatio = "") %>%
  left_join(redTeamLosses, by = c("blueTeamTag" = "redTeamTag")) 
View(teamLosses)
```

```{r}
teamWinLossRatio <- teamWins %>%
  left_join(teamLosses, by = c("blueTeamTag" = "blueTeamTag")) %>%
  mutate(TotalWins = (teamWinLossRatio$WinsPerTeam.x + teamWinLossRatio$WinsPerTeam.y)) %>%
  mutate(TotalLosses = (teamWinLossRatio$LossesPerTeam.x + teamWinLossRatio$LossesPerTeam.y)) %>%
  mutate(TotalGames = teamWinLossRatio$TotalWins + teamWinLossRatio$TotalLosses) %>%
  mutate(WinRatio = teamWinLossRatio$TotalWins / teamWinLossRatio$TotalGames)
  
View(teamWinLossRatio)
```


```{r}
g_WinRatio <- ggplot(data = teamWinLossRatio, aes(x = teamWinLossRatio$blueTeamTag, y = teamWinLossRatio$WinRatio)) + geom_bar(stat = "identity")
g_WinRatio 
#+ coord_flip() + scale_y_discrete(expand = c(0, 0), limits = lim) 
# + ggrepel::geom_label_repel(aes(x = teamWinLossRatio$blueTeamTag), label = rownames(teamWinLossRatio))
  #theme(text = element_text(size = 10))
  #scale_x_discrete(aes(x = teamWinLossRatio$blueTeamTag), expand = c(0,0.6))
```

#So now we finally have the Win/Loss Ratio of pro teams from 2015-2017 (3 Seasons)
#Now we have to look at games where baron was slain, find the victors of those, and see if it compares

```{r}
#find the games with Baron results

gamesWithBaronData <- X_LeagueofLegends %>%
  select(blueTeamTag, bResult, rResult, redTeamTag, bBarons, rBarons)
View(gamesWithBaronData)

```

```{r}
#filter out games where no team got baron

gamesWithBaron <- gamesWithBaronData %>%
filter(!(gamesWithBaron$bBarons == '[]' & gamesWithBaron$rBarons == '[]')) 
View(gamesWithBaron)
```

```{r}
#give each team a baron score, based on how many barons they have slain
gamesWithBaronScores <- gamesWithBaron %>%
  #mutate(bBaronsNoBrackets = gsub("\\[|\\]", "", gamesWithBaron$bBarons), rBaronsNoBrackets = gsub("\\[|\\]", "", gamesWithBaron$rBarons))
mutate(bBaronScore = 0, rBaronScore = 0)


#x = strsplit(gamesWithBaronNoBrackets$bBaronsNoBrackets, ", ")
x = gamesWithBaronScores$bBarons;
y = gamesWithBaronScores$rBarons;

for(i in 1:length(x))
{
  #each time there is a comma, add one to baron score
  if(x[i] != '[]')
  {
    gamesWithBaronScores$bBaronScore[i] = (str_count(x[i], "\\,") + 1)
  }
}

for(i in 1:length(y))
{
  #each time there is a comma, add one to baron score
  if(y[i] != '[]')
  {
    gamesWithBaronScores$rBaronScore[i] = (str_count(y[i], "\\,") + 1)
  }
}


View(gamesWithBaronScores)
```

#now that we have a Baron score for each game, we need to figure give each team a baron score

```{r}
#count of the amount of barons per team on BLUE SIDE
blueTeamBarons <- gamesWithBaronScores %>%
  select(blueTeamTag, bBaronScore) %>%
  group_by(blueTeamTag) %>%
  summarise(baronsPerTeam = sum(bBaronScore))
  View(blueTeamBarons)
```

```{r}
#count of the amount of barons per team on RED SIDE
redTeamBarons <- gamesWithBaronScores %>%
  select(redTeamTag, rBaronScore) %>%
  group_by(redTeamTag) %>%
  summarise(baronsPerTeam = sum(rBaronScore))
  View(redTeamBarons)
```

```{r}
teamBaronScore <- blueTeamBarons %>%
  left_join(redTeamBarons, by = c("blueTeamTag" = "redTeamTag")) %>%
  mutate(TotalBarons = (teamBaronScore$baronsPerTeam.x + teamBaronScore$baronsPerTeam.y))
  #mutate(TotalGames = teamWinLossRatio$TotalGames, baronsPerGame = TotalBarons / TotalGames)
View(teamBaronScore)
```

```{r}
teamsData <- teamBaronScore %>%
  left_join(teamWinLossRatio, by = c("blueTeamTag" = "blueTeamTag")) %>%
  mutate(baronsPerGame = TotalBarons / TotalGames)
View(teamsData)
```

```{r}
g_BaronAverage <- ggplot(data = teamsData, aes(x = teamsData$blueTeamTag, y = teamsData$baronsPerGame)) + geom_bar(stat = "identity")
g_BaronAverage
```

#so now we can see how many Barons each team yielded from 2015-2017; let's see if that graph compares to their win ratio

```{r}
g_BaronScores <- ggplot(data = teamBaronScore, aes(x = teamBaronScore$blueTeamTag, y = teamBaronScore$TotalBarons)) + geom_bar(stat = "identity")
g_BaronScores
```

#it appears that the two graphs slightly correlate, not strongly though. Obviously, correlation doesn't imply causation, but SKT both has highest win rate AND highest BaronScore, however, there are most likely lurking and cofounding variables: gold, kills, towers, mood, attitude, communication; so it's hard to tell if Baron truly is the cause for victories

```{r}
#Let's get our bootstrap confidence interval. 95%

rsq <- function(formula, data, indices) 
{
  d <- data[indices,] # allows boot to select sample 
  fit <- lm(formula, data = d)
  return(summary(fit)$r.square)
}

results <- boot(data = teamsData, statistic = rsq, 
  	R=1000, formula = teamsData$WinRatio~teamsData$baronsPerGame)

results 
plot(results)

boot.ci(results, type = "bca")

```


